---
title: "Assignment 06 - EDA"
author: "Scott Stoltzman"
date: "5/29/2019"
output: html_document
---


# Do your EDA Work in this file!

# Data-Science-Certificate-Assignment-06
Exploratory data analysis (EDA)

## Assignment:  

  - Open `Assignment 06 - EDA.Rmd`
  - Do EDA and come up with an interesting analysis to chase down
    - List all of your questions (you don't necessarily have to answer them all)
  - You must:
    - Utilize `ggplot` plotting
    - Use `dplyr` data manipulation
    - Use `if_else` within a `mutate` function
    - Use `group_by` and `summarize`
    
Choose a data set from one of the following:  

  - [Black Friday](https://www.kaggle.com/mehdidag/black-friday)
  - [Wine Reviews](https://www.kaggle.com/zynicide/wine-reviews)
  - [LA Parking Citations](https://www.kaggle.com/cityofLA/los-angeles-parking-citations)

### Hint: download a csv and then use the readr::read_csv('your_file_location')
```{r}
library(tidyverse)
```

```{r}
dat <- readr::read_csv("winemag-data-130k-v2.csv")
```

```{r}
summary(dat)

```

```{r}
ggplot(data = winedat) + 
  geom_bar(mapping = aes(x = country)) + 
  coord_flip()



```


```{r}
  
countrydat <- dat %>%
  group_by(country) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(country1000= if_else(n >= 1000,country,'Rest'))
```




```{r}
varietydat <- dat %>%
  group_by(variety) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(variety1000= ifelse(n >= 1000,variety,'Rest'))
```

```{r}
tasterdat <- winedat %>%
  group_by(taster_name) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(taster = if_else(is.na(taster_name), 'Unknown', taster_name))
  
```

```{r}
winejoindat1 <-
left_join(winedat, countrydat, by = c("country" = "country"))

```

```{r}
winejoindat2 <-
  left_join(winejoindat1, varietydat, by = c("variety" = "variety"))
```


```{r}
winejoindat3 <-
  left_join(winejoindat2, tasterdat, by = c("taster_name" = "taster_name"))
```

```{r}
coolwinedat <-
    select(winejoindat3, points, price, country1000, variety1000, taster)
```

```{r}
library(data.table)
coolwinedat <- rename(coolwinedat, 'Country' = country1000,'Points' = points, 'Price' = price, 'Variety' = variety1000, 'Taster' = taster)
coolwinedat
```

```{r}
summary(coolwinedat)
```

```{r}
coolwinedat <- na.omit(coolwinedat)
summary(coolwinedat)
```

```{r}
ggplot(coolwinedat, aes(x= Points, y = Price, color = Country))+
  geom_point()
```

```{r}
ggplot(coolwinedat, aes(x= Country, y = Price, color = Points))+
  geom_point()+
  coord_flip()
```

## I want to try and figure out how to do all those steps before into one group of code:

```{r}
library(tidyverse)
dat <- readr::read_csv("winemag-data-130k-v2.csv")

countrydat <- dat %>%
  group_by(country) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(country1000= if_else(n >= 1000,country,'Rest'))

varietydat <- dat %>%
  group_by(variety) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(variety1000= ifelse(n >= 1000,variety,'Rest'))

tasterdat <- winedat %>%
  group_by(taster_name) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(taster = if_else(is.na(taster_name), 'Unknown', taster_name))

sweetdat <-
left_join(winedat, countrydat, by = c("country" = "country"))

sweetdat <-
  left_join(sweetdat, varietydat, by = c("variety" = "variety"))

sweetdat <-
  left_join(sweetdat, tasterdat, by = c("taster_name" = "taster_name"))

sweetdat <- na.omit(sweetdat)
summary(sweetdat)
  
```

