---
title: "Assignment 06 - EDA"
author: "Scott Stoltzman"
date: "5/29/2019"
output: html_document
---


# Do your EDA Work in this file!

# Data-Science-Certificate-Assignment-06
Exploratory data analysis (EDA)

## Assignment:  

  - Open `Assignment 06 - EDA.Rmd`
  - Do EDA and come up with an interesting analysis to chase down
    - List all of your questions (you don't necessarily have to answer them all)
  - You must:
    - Utilize `ggplot` plotting
    - Use `dplyr` data manipulation
    - Use `if_else` within a `mutate` function
    - Use `group_by` and `summarize`
    
Choose a data set from one of the following:  

  - [Black Friday](https://www.kaggle.com/mehdidag/black-friday)
  - [Wine Reviews](https://www.kaggle.com/zynicide/wine-reviews)
  - [LA Parking Citations](https://www.kaggle.com/cityofLA/los-angeles-parking-citations)

### Hint: download a csv and then use the readr::read_csv('your_file_location')




## I want to try and figure out how to do all those steps before into one group of code:

```{r}
library(tidyverse)
dat <- readr::read_csv("winemag-data-130k-v2.csv")

countrydat <- dat %>%
  group_by(country) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(country1000= if_else(n >= 1000,country,'Rest'))%>%
  mutate(countryn= n)

varietydat <- dat %>%
  group_by(variety) %>%
  summarize (n= n()) %>%
  mutate(pct_n = n / sum(n))%>%
  arrange(desc(n)) %>%
  mutate(pct_n_running = cumsum(pct_n)) %>%
  mutate(variety1000= ifelse(n >= 1000,variety,'Rest')) %>%
  mutate(varietyn= n)

tasterdat <- winedat %>%
  group_by(taster_name) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(taster = if_else(is.na(taster_name), 'Unknown', taster_name)) %>%
  mutate(tastern= n)

sweetdat <-
left_join(winedat, countrydat, by = c("country" = "country"))

sweetdat <-
  left_join(sweetdat, varietydat, by = c("variety" = "variety"))

sweetdat <-
  left_join(sweetdat, tasterdat, by = c("taster_name" = "taster_name"))

sweetdat <-
    select(sweetdat, points, price, country1000, countryn, variety1000, varietyn, taster, tastern)

sweetdat <- rename(sweetdat, 'country' = country1000,'variety' = variety1000)

sweetdat <- na.omit(sweetdat)


  

summary(sweetdat)
  
```


##Looking at Price vs Points

```{r}
ggplot(sweetdat, aes(x= points, y = price))+
  geom_smooth()+
  geom_point()
```


```{r}
ggplot(filter(sweetdat, price <= 500), aes(x= points, y = price))+
  geom_smooth()+
  geom_point()
```


A quick look shows that 
```{r}
ggplot(sweetdat, aes(x= points, y = price, color = country))+
  geom_point()+
  geom_smooth()

```

```{r}
ggplot(filter(sweetdat, price <= 500), aes(x= points, y = price, color = country))+
  geom_point()+
  geom_smooth()

```

#Facet Wrap with price under $1000



```{r}
ggplot(filter(sweetdat, price<=500), aes(x= points, y = price, color = country))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~country)
```


```{r}
ggplot(sweetdat, aes(x= points, y = price, color = country))+
  geom_point()+
  facet_wrap(~taster)
```


♣
```{r}
ggplot(filter(sweetdat, price<=500), aes(x= points, y = price, color = country))+
  geom_point()+
  facet_wrap(~taster)
```



```{r}
ggplot(data = sweetdat)+
geom_bar(mapping = aes(x= reorder(taster,tastern), fill = country, color = country))+
  coord_flip()+
  labs(x = "Taster", y= "Reviews")

```


```{r}
ggplot(data = sweetdat)+
geom_bar(mapping = aes(x= reorder(variety,varietyn), fill = country, color = country))+
  coord_flip()+
    labs(x = "Variety", y= "Reviews")
```

```{r}
ggplot(data = sweetdat)+
geom_bar(mapping = aes(x= reorder(variety,varietyn), fill = taster, color = taster))+
  coord_flip()+
    labs(x = "Variety", y= "Reviews")

```



```{r}
ggplot(data = sweetdat)+
  stat_summary(mapping = aes(x = reorder(variety,desc(variety)), y = price))+
  coord_flip()+
  labs(x = "Variety", y = "Price")

```


```{r}
ggplot(data = sweetdat)+
  stat_summary(mapping = aes(x = reorder(country,desc(country)), y = price))+
  coord_flip()+
  labs(x = "Country", y = "Price")

```

```{r}
ggplot(data = sweetdat)+
  stat_summary(mapping = aes(x = reorder(taster,desc(taster)), y = price))+
  coord_flip()+
  labs(x = "Reviewer", y = "Price")

```

